---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# Data Quality Checks

<!-- badges: start -->
<!-- badges: end -->

`{dqc}` aims to create a simple and intuitive data quality check API.

## Installation

You can install the development version of `{dqc}` like so:

``` r
# devtools::install_github('colin-fraser/dqc')
```

## Example

This is a basic example which shows you how to solve a common problem:

```{r example}
library(dqc)

mtcars_check_suite <- dqc_suite(
  check_between(mpg, 0, 40),
  check_values_in(vs, c(0, 1))
)
mtcars_check_suite(mtcars)
```

The `quick_checks` interface can be useful, especially when reading data in through a pipeline.

```{r}
df <- mtcars %>% 
  quick_check(
    check_between(mpg, 10, 30),
    check_no_na(gear),
    check_names(c("mpg", "cyl", "disp", "hp", "drat", "wt", "qsec", "vs", "am", 
"gear", "carb"))
  )
```

By default, `quick_check` informs you about data quality check failures but does not impede your work, returning its input without changes.

```{r}
head(df)
```

But this can be changed.

```{r, error=TRUE}
df <- mtcars %>% 
  quick_check(
    check_between(mpg, 10, 30),
    check_no_na(gear),
    .behavior = 'stop'
  )
```
